### 2020-04-20 final_report/methodology.tex
make tables smaller to clear space

\begin{table}[h]
	\centering
	\begin{tabular}{llrl}
	\toprule
	Regression performance metrics	& Mathematical formulation / description &
	\multicolumn{2}{c}{Ideal value} \\
	\midrule
	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
								& [TBR] \\
	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
	\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
	Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
	Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
	\midrule
	Evaluation time metrics	& {} & {} & {} \\
	\midrule
	Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
	$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
	Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
	$\hat{f}(x)$})/N$	& 0 & [ms] \\
	Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
	(N\overline{t}_{\text{pred.}})$	&
	$\to\infty$ & [rel.] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{llll}
	\toprule
	Surrogate & Acronym & Implementation & Hyperparameters \\
	\midrule
	Support vector machines	& SVM & SciKit Learn & TODO \\
	Gradient boosted trees	& GBT & SciKit Learn & TODO \\
	Extremely random trees	& ERT & SciKit Learn & TODO \\
	AdaBoost	& AB & SciKit Learn & TODO \\
	Gaussian process regression	& GPR & SciKit Learn & TODO \\
	$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
	Neural networks	& NN & Keras (TensorFlow) & TODO \\
	Inverse distance weighing & IDW & SMT & TODO \\
	Radial basis functions & RBF & SMT & TODO \\
	Stochastic gradient descent & SGD & SciKit Learn & TODO \\
	Ridge regression & RR & SciKit Learn & TODO \\
	Kriging & KRG & SMT & TODO \\
	\bottomrule
	\end{tabular}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llrl}
		\toprule
		Regression performance metrics	& Mathematical formulation / description &
		\multicolumn{2}{c}{Ideal value} \\
		\midrule
		Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
									& [TBR] \\
		Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
		Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
		Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
		\midrule
		Evaluation time metrics	& {} & {} & {} \\
		\midrule
		Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
		Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
		$\hat{f}(x)$})/N$	& 0 & [ms] \\
		Relative speedup	& $(\text{wall evaluation time of $f(x)$}) /
		(N\overline{t}_{\text{pred.}})$	&
		$\to\infty$ & [rel.] \\
		\bottomrule
		\end{tabular}
	}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

@@

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn & TODO \\
		Gradient boosted trees	& GBT & SciKit Learn & TODO \\
		Extremely randomized trees	& ERT & SciKit Learn & TODO \\
		AdaBoosted decision trees	& AB & SciKit Learn & TODO \\
		Gaussian process regression	& GPR & SciKit Learn & TODO \\
		$k$ nearest neighbours	& KNN & SciKit Learn & TODO \\
		Neural networks	& NN & Keras (TensorFlow) & TODO \\
		Inverse distance weighing & IDW & SMT & TODO \\
		Radial basis functions & RBF & SMT & TODO \\
		Stochastic gradient descent & SGD & SciKit Learn & TODO \\
		Ridge regression & RR & SciKit Learn & TODO \\
		Kriging & KRG & SMT & TODO \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}
